\chapter{Conclusion and further work}
In this project several aspects of robotics have been considered. The first topic is visualization and simulation where a virtual model of a given robot is made. This includes measurements, mass and moments of inertia. Some of the measurements and mass is only guessed or estimated and it may not result in a perfect recreation of the actual robot. The inertia is also made based on simplifications and if one want a more realistic behaviour of the robot it may be by recalculating this. The simulation environment Gazebo is a good software with much support online in forums and wikis. There was however some trouble when implementing the moments of inertia that would lead to the robot not spawning properly, because of too low inertia of the two fingers.\\\\
The second part that was presented was the kinematics problem where the forward kinematics was found. The DH convention was used to find this. Then the forward kinematics problem were solved by using the MATLAB robotics toolbox\cite{MatlabRobTool}. The toolbox gave very good and precise solutions and was very easy to use. One thing that may not be so good is that it uses about 100ms per set point which may be too slow for an online planner, but if offline planning is the purpose the time consumption does not matter.
\\\\
The next part is the control and motion planning. The PD controller with gravity compensation is a very basic controller which worked very well for this case, but a better controller should be considered. Both \cite{spong} and \cite{Siciliano} are good resources when considering more advanced controllers. This project includes a way to plan a simple path with a single obstacle present in it. The trajectory is not found though, because of the obstacle one does not want only the end effector to avoid the obstacle, but the rest of the robot manipulator must avoid it as well which is a more complex problem and should be included in further work. In fact the motion planning is a very complex task and \cite{spong} states that path and trajectory planning is one of the most difficult problems in computer science.